High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-08 notebooks/mnist.qmd
done

```{julia}
# Hyper:
_retrain = false
_regen = false

@@

```{julia}
# Model parameters:
epochs = 10
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 128
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                        # finaliser function
```

>>>>

```{julia}
# Hyper:
_retrain = true
_regen = true

@@

```{julia}
# Model parameters:
epochs = 25
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 128
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                        # finaliser function
```
